Spfy: an integrated graph database for real-time prediction of Escherichia coli phenotypes and downstream comparative analyses

### 2018-03-01 paper-webserver.tex
caption

\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/docker}
\end{center}
\caption{The various Docker containers used in Spfy. Arrows represent the connections between different containers, and the entire platform can be recreated with a single command using Docker-Compose.}
\label{fig-docker}
\end{figure}

>>>>

\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/docker}
\end{center}
\caption{The various Docker containers used in Spfy. Arrows represent the connections between different containers, and the entire platform can be recreated with a single command using its Docker-Compose definition.}
\label{fig-docker}
\end{figure}
